---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(data.tree)
```
# wsta_google_maps

The purpose of this repository is to house the final and supporting documents for moving the Winston-Salem Transit Authority bus maps into the Google Transit Partners framework. Moving this data into google will allow citizens of Winston-Salem to use googlemaps to learn more about bus routes and consider public transit when planning their transportation. Additionally, this allows google maps to be used for analysis of the transportation system as a whole.

# Resources:

## WSTA

[Route Overview](https://wstransit.com/bus-routes/)

## Google Transit Partners

[Definitions](https://developers.google.com/transit/gtfs/reference/#term-definitions)

[Examples](https://developers.google.com/transit/gtfs/examples/gtfs-feed)

[Testing Environment](https://github.com/google/transitfeed/wiki/ScheduleViewer)

[feed validator](https://github.com/google/transitfeed/wiki/FeedValidator)

[CARTA Chattanooga System](http://www.gocarta.org/alt-flash/insidecarta.php#developers)

## Shape File Creator

[https://www.gmap-pedometer.com/](https://www.gmap-pedometer.com/)


# Repository Structure

```{r echo=FALSE}
acme <- Node$new("WSTA Transit")
  accounting <- acme$AddChild("routes")
  routes_more <- accounting$AddChild("Route GPX files")
  research <- acme$AddChild("references")
    newProductLine <- research$AddChild("Google Provided Examples")
    newProductchata <- research$AddChild("Chattanooga CARTA Examples")
  it <- acme$AddChild("src")
    outsource <- it$AddChild("Scripts to Generate Files")
  out <- acme$AddChild("out")
  agency <- out$AddChild("agency.txt")
  stops <- out$AddChild("stops.txt")
  routes <- out$AddChild("routes.txt")
  trips <- out$AddChild("trips.txt")
  stop_times <- out$AddChild("stop_times.txt")
  calendar <- out$AddChild("calendar.txt")
  shapes <- out$AddChild("shapes.txt")
    
    print(acme)

```

